Untrusted B2B Collaboration using the Blockchain

### 2018-07-25 paper/paper.tex
Small review changes

With the increasing spread of Blockchain technology, this problem could be rectified.
A Blockchain is a decentralized information-storage network. Information is stored in blocks, which are chained together via cryptograhic means. This means, that many participants can agree on a common public state of information without trusting each other. This technology is commonly used to realize virtual currencies, also called cryptocurrencies.
Ethereum is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
Smart contracts are small programs, which are ran by the Blockchain network. They have very limited processing power, but they enable the execution of code which has a commonly known state.

@@

The interaction of the components can be seen in Figure \ref{fig:system_diagram}.

>>>>

With the increasing spread of Blockchain technology, this problem could be rectified.
A Blockchain is a decentralized information-storage network. Information is stored in blocks, which are chained together via cryptograhic means. This means, that many participants can agree on a common public state of information without trusting each other. This technology is commonly used to realize virtual currencies, also called cryptocurrencies.
Ethereum \cite{wood2014ethereum} is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
Smart contracts are small programs, which are ran by the Blockchain network. They have very limited processing power, but they enable the execution of code which has a commonly known state.

@@

The structure of components for one organization can be seen in Figure \ref{fig:system_diagram}.
